Technical Report

### 2024-02-28 Reports/tech_report1.tex
update
update report

@@

>>>>

\subsection{Find best open ReLU for layer 7 for normal 5x100, new pure y-constraints}

@@

	\item \emph{Key results:} Actually, even 78,81 nodes have not reach the turning point. So the follow-up tests will use 81 node. $\gamma$ for different open numbers are

\section{February 27 experiments}

\subsection{Compute gamma for layer 7 for normal 5x100, pure y-constraints}

This experiment is to compute the gamma of layer 7 normal 5x100 with pure-y constraints constraints, with open 81 node.

The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|. And the partial output file name is \verb*|DL_V0p3_layer7_open_81_node_2.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 81 ReLU.

\begin{itemize}
	\item\emph{Experiments Id}: 022700102024

	\item\emph{Open $\ReLU$ number:} Open 81 ReLU node

	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_22_15_37_07.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 5 using the latest method. 
\end{itemize}

\begin{itemize}
	\item \emph{Log:} \verb*|DL_V0p3_layer7_open_81_node_2.txt|.

	\item \emph{Total time:} 36033.7s.

	\item \emph{Key results:}  The average gamma of this layer is:  2.9401721224547486

	The average solution for gamma of this layer is:  2.7865989645659845.

	\item  \emph{Binary output}: The gamma of layer 7 is stored in the file \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_27_18_03_13.b|.
